### 2017-10-31 1/exams/m2-practice.tex
Moving README.
Start of practice exam soln.

\vskip 2.5in

\begin{SaveVerbatim}{VerbEnv}  
SOLUTION:
\end{SaveVerbatim}

@@

\begin{verbatim}
;; f :

@@

;; g :

@@

;; h :

@@

;; i :

@@

;; j :

@@

;; k :

@@

@@

@@

\begin{SaveVerbatim}{VerbEnv}

SOLUTION:

\end{SaveVerbatim}

@@

@@

\begin{verbatim}
;; A Tournament is one of:
;; - String
;; - (make-bracket Tournament Tournament)
;; Interp: a sports tournament where a String is a team name
;; that is still in the tournament and a bracket represents
;; a match between the winner of two tournaments. 
\end{verbatim}

@@

>>>>

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

(define (f b s) s)
(define (g fs) (fs #false))
(define (h bs ns) 2)
(define (i f) (f 2))
(define (j xs) (map f xs))
(define (k f g x) (g (f x)))
\end{SaveVerbatim}

@@

\begin{verbatim}
;; f : \censor{Number -> Number}

@@

;; g : \censor{[Listof Number] -> [Listof Number]}

@@

;; h : \censor{[Listof Number] [Listof Number] -> [Listof Number]}

@@

;; i : \censor{(Number -> Number) -> Number}

@@

;; j : \censor{Number -> (Number -> Number)}

@@

;; k : \censor{[X] (Natural -> X) Natural -> [Listof X]}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

;; avg : [Listof Number] -> Number
;; Compute the average of a list of numbers
;; Assume: the list is non-empty
(check-expect (avg (list 3 4 5)) 4)
(check-expect (avg (list 10 20)) 15)
(define (avg lon)
  (/ (sum lon) 
     (length lon)))

;; sum : [Listof Number] -> Number
;; Sum the list of numbers
(check-expect (sum '()) 0)
(check-expect (sum (list 3 4 5)) 12)
(define (sum lon)
  (foldr + 0 lon))

;; Alt: follow [Listof Number] template
\end{SaveVerbatim}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

;; mostest : [X] [NEListof X] [X X -> X] -> X
;; Produce the first most-est element in the list
(define (mostest xs most)
  (cond [(empty? (rest xs)) (first xs)]
        [else
          (most (first xs)
                (mostest (rest xs) most))]))

(define (longest los)
  (mostest los longer))

(define (smallest lon)
  (mostest lon min))
\end{SaveVerbatim}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

;; count-pos : [Listof Number] -> Number
;; Count the number of non-negative numbers in given list
(check-expect (count-pos '()) 0)
(check-expect (count-pos (list 3 -1 0 2)) 2)
(define (count-pos lon)
  (foldr (lambda (n c) (if (positive? n) (add1 c) c)) 0 lon))

;; Alt:
(define (count-pos lon)
  (length (filter positive? lon)))
\end{SaveVerbatim}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

(define (map f xs)
  (foldr (lambda (x ys) (cons (f x) ys)) '() xs))
\end{SaveVerbatim}

@@

\begin{verbatim}
;; A Tournament is one of:
;; - String
;; - (make-bracket Tournament Tournament)
;; Interp: a sports tournament where a String is a team name
;; that is still in the tournament and a bracket represents
;; a match between the winner of two tournaments. 
(define-struct bracket (t1 t2))
\end{verbatim}

@@

\begin{SaveVerbatim}{VerbEnv}
SOLUTION:

;; most-games : Tournament -> Number
;; Compute most games any team has to win to win tournament
(check-expect (most-games "NY") 0)
(check-expect (most-games (make-bracket "LA" "HOU")) 1)
(check-expect (most-games (make-bracket (make-bracket "LA" "DC") "HOU")) 2)
(define (most-games t)
  (cond [(string? t) 0]
        [(bracket? t)
         (add1 (max (most-games(bracket-t1 t))
                    (most-games(bracket-t2 t))))]))
\end{SaveVerbatim}
